### 2012-10-25 inst/examples/reed-example.Rmd
Reed example showing basic use of a GP in SDP

@@

Noise function 
```{r}
z_g <- function(sigma_g) rlnorm(1, 0, sigma_g) #1+(2*runif(1, 0,  1)-1)*sigma_g #
```

@@

```{r}
x_grid = seq(0, 1.5 * K, length=100)
T <- 40
sigma_g <- 0.1
x <- numeric(T)
x[1] <- 1
```

@@

```{r}
for(t in 1:(T-1))
  x[t+1] = z_g(sigma_g) * f(x[t], h=0, p=p)

plot(x)
```

@@

```{r}
obs <- data.frame(x=x[1:(T-1)],y=x[2:T])
X <- x_grid
library(nonparametricbayes)
gp <- gp_fit(obs, X, c(sigma_n=1, l=1))
```

@@

## Another example using the May model

```{r}
f <- May
p <- c(r = .75, k = 10, a=1.2, H=1, Q = 3)
K <- 8 # approx
```

Model dynamics look like this:

```{r}
birth <- function(x) p["r"] * (1-  x / p["k"])
death <- function(x) p["a"] * x ^ (p["Q"] - 1) / (x ^ p["Q"] + p["H"])
df <- data.frame(x = x_grid, b = sapply(x_grid, birth), d = sapply(x_grid, death))
ggplot(df) + geom_line(aes(x, b), col = "blue") + geom_line(aes(x,d), col = "red")
````

```{r}
x[1] = 2.5
for(t in 1:(T-1))
  x[t+1] = z_g(sigma_g) * f(x[t], h=0, p=p)
plot(x)
```

```{r}
obs <- data.frame(x=x[1:(T-1)],y=x[2:T])
X <- x_grid
gp <- gp_fit(obs, X, c(sigma_n=1, l=1))
```

Gaussian Process inference from this model

```{r}
df <- data.frame(x=X, y=gp$Ef, ymin=(gp$Ef-2*sqrt(abs(diag(gp$Cf)))), ymax=(gp$Ef+2*sqrt(abs(diag(gp$Cf)))))
true <- data.frame(x=X, y=sapply(X,f, 0, p))
ggplot(df)  + geom_ribbon(aes(x,y,ymin=ymin,ymax=ymax), fill="gray80") +
  geom_line(aes(x,y)) + geom_point(data=obs, aes(x,y)) +
  geom_line(data=true, aes(x,y), col='red', lty=2)
```

## Further steps

* is the posterior GP capturing the process noise?
* Need to add optimization over hyperparameters

>>>>

### Beverton-Holt function

@@

@@

```{r}
x_grid = seq(0, 1.5 * K, length=101)
T <- 40
sigma_g <- 0.1
x <- numeric(T)
x[1] <- 1
```

Noise function, profit function
```{r}
z_g <- function() rlnorm(1, 0, sigma_g) #1+(2*runif(1, 0,  1)-1)*sigma_g #
profit <- profit_harvest(1,0,0)
```

@@

```{r}
for(t in 1:(T-1))
  x[t+1] = z_g() * f(x[t], h=0, p=p)
```

@@

```{r}
obs <- data.frame(x=x[1:(T-1)],y=x[2:T])
X <- x_grid
library(nonparametricbayes)
gp <- gp_fit(obs, X, c(sigma_n=.5, l=1.5))
```

@@

## Stochastic Dynamic programming solution based on the posterior Gaussian process:

```{r}
rownorm <- function(M) t(apply(M, 1, function(x) x/sum(x)))
h_grid <- x_grid
```

Define a transition matrix $F$ from the Gaussian process, giving the probability of going from state $x_t$ to $x_{t+1}$.
We already have the Gaussian process mean and variance predicted for each point $x$ on our grid, so this is simply:

```{r}
V <- sqrt(diag(gp$Cf))
matrices_gp <- lapply(h_grid, function(h){
  F <- sapply(x_grid, function(x) dnorm(x, gp$Ef-h, V))
  F <- rownorm(F)
})
```

True $f(x)$

```{r}
matrices_true <- lapply(h_grid, function(h){
  mu <- sapply(x_grid, f, h, p)
  F_true <- sapply(x_grid, function(x) dnorm(x, mu, sigma_g))
  F_true <- rownorm(F_true)
})
```

Calculate the policy function using the true F:

```{r}
opt_true <- find_dp_optim(matrices_true, x_grid, h_grid, 20, 0, profit, delta=.01)
```

Calculate using the inferred GP

```{r}
opt_gp <- find_dp_optim(matrices_gp, x_grid, h_grid, 20, 0, profit, delta=.01)
```

```{r}
require(reshape2)
policies <- melt(data.frame(stock=x_grid, GP = x_grid[opt_gp$D[,1]], Exact = x_grid[opt_true$D[,1]]), id="stock")
q1 <- ggplot(policies, aes(stock, stock - value, color=variable)) + geom_point() + xlab("stock size") + ylab("escapement") 
q1
```

We can see what happens when we attempt to manage a stock using this:

``` {r othernoise}
z_g <- function() rlnorm(1,0, sigma_g)
````

``` {r  simulate }
set.seed(1)
sim_gp <- ForwardSimulate(f, p, x_grid, h_grid, K, opt_gp$D, z_g, profit=profit)
set.seed(1)
sim_true <- ForwardSimulate(f, p, x_grid, h_grid, K, opt_true$D, z_g, profit=profit)
````

``` {r  simplot}
df <- data.frame(time = sim_gp$time, stock_gp = sim_gp$fishstock, stock_true = sim_true$fishstock, harvest_gp = sim_gp$harvest, havest_true = sim_true$harvest)
df <- melt(df, id="time")
ggplot(df) + geom_line(aes(time,value, color=variable))
````

Total Profits

```{r}
sum(sim_gp$profit)
sum(sim_true$profit)
```
